\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{float}
\title{4D Tetris - Voice of Customer Questionnaire}
\date{}

\begin{document}

\maketitle

\begin{multicols}{2}

    \renewcommand{\labelitemi}{\textsc{\ding{111}}}

\begin{enumerate}
    \item \textbf{Is the idea of a 4D Tetris game interesting?}
    \begin{itemize}
        \item Very Interesting
        \item Somewhat Interesting
        \item Neutral
        \item Not Very Interesting
        \item Not at All Interesting
    \end{itemize}

    \item \textbf{Are the keybindings too complicated? (see back)}
    \begin{itemize}
        \item Too Complicated
        \item Slightly Complicated
        \item Just Right
        \item Too Simple
    \end{itemize}

    \item \textbf{Is the chosen graphical style appropriate?}
    \begin{itemize}
        \item Yes
        \item No, should be more colorful
        \item No, should be more minimalistic
        \item No, should be more complex
    \end{itemize}

    \item \textbf{Does the concept sound interesting?}
    \begin{itemize}
        \item Very Exciting
        \item Somewhat Exciting
        \item Neutral
        \item Not Exciting
    \end{itemize}
    \newcolumn
    \item \textbf{How would you like level progression to go?}
    \begin{itemize}
        \item Faster Speed
        \item More Complicated Pieces
        \item Additional Mechanics
        \item Other
    \end{itemize}

    \item \textbf{How much prior experience do you have with Tetris?}
    \begin{itemize}
        \item None
        \item Casual (Played occasionally)
        \item Experienced (Plays often)
        \item Expert (Plays competitively or deeply understands mechanics)
    \end{itemize}

    \item \textbf{Would you prefer a tutorial to understand 4D mechanics?}
    \begin{itemize}
        \item Yes, a step-by-step tutorial
        \item Yes, but a quick explanation is fine
        \item No, I'd rather figure it out
    \end{itemize}

    \item \textbf{What kind of graphical style do you prefer?}
    \begin{itemize}
        \item Classic retro (pixel-based, minimal shading)
        \item Neon futuristic (glowing edges, cyberpunk aesthetic)
        \item Abstract minimalism (clean lines, geometric shapes)
        \item Other \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    \end{itemize}
\end{enumerate}
\end{multicols}
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    Modifier & LEFT & UP & RIGHT& DOWN\\
    \hline
     & Move left & Move up & Move right & Move down\\
    A & XY- & XZ+ & XY+ & XZ-\\
    S & XW- & YZ+ & XW+ & YZ-\\
    D & YW- & ZW+ & YW+ & ZW-\\
    \hline
    \end{tabular}
    \caption{Input Layout: The arrow keys are used to move the piece, the A, S, D keys are used to modify the plane of rotation.}
    \label{tab:input}
\end{table}
\end{document}
