\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{pifont}
\title{4D Tetris - Final Gameplay Testing Questionnaire}
\date{}

\begin{document}
\section*{Final Gameplay Testing Questionnaire}
\renewcommand{\labelitemi}{\textsc{\ding{111}}}

\begin{multicols}{2}
\begin{enumerate}

    \item \textbf{How would you rate the overall gameplay experience?}
    \begin{itemize}
        \item Excellent
        \item Good
        \item Neutral
        \item Poor
        \item Terrible
    \end{itemize}

    \item \textbf{Was it clear how to play the game?}
    \begin{itemize}
        \item Very Clear
        \item Mostly Clear
        \item Somewhat Confusing
        \item Very Confusing
    \end{itemize}

    \item \textbf{How difficult did the game feel?}
    \begin{itemize}
        \item Too Easy
        \item Just Right
        \item Somewhat Challenging
        \item Very Difficult
    \end{itemize}

    \item \textbf{How would you rate the 4D controls?}
    \begin{itemize}
        \item Very Intuitive
        \item Slightly Confusing
        \item Confusing
        \item Frustrating
    \end{itemize}

    \item \textbf{Were the keybindings easy to use?}
    \begin{itemize}
        \item Yes
        \item No, too many
    \end{itemize}

    \item \textbf{Did the game feel fair and skill-based?}
    \begin{itemize}
        \item Yes
        \item Somewhat
        \item No
    \end{itemize}

    \item \textbf{How would you rate the visual presentation?}
    \begin{itemize}
        \item Excellent
        \item Good
        \item Neutral
        \item Needs Improvement
    \end{itemize}

    \item \textbf{Did you experience any bugs or crashes?}
    \begin{itemize}
        \item No
        \item Yes, minor
        \item Yes, major
    \end{itemize}

    \item \textbf{Would you recommend this game to others?}
    \begin{itemize}
        \item Definitely
        \item Maybe
        \item No
    \end{itemize}

\end{enumerate}
\end{multicols}

\vspace{1em}
\noindent\textbf{If you encountered bugs, please describe them below:}
\vspace{2em}
\noindent\rule{0.8\textwidth}{0.4pt}
\vspace{2em}
\noindent\rule{1.0\textwidth}{0.4pt}

\vspace{5cm}




\end{document}